Dirac neutrino mass generation from Majorana messenger

### 2019-07-07 draft.tex
Updates from Overleaf

\author{First Author\footnote{\href{mailto:first@author}{first@author}},
Second Author\footnote{\href{mailto:second@author}{second@author}}\\
\textit{\small  First Institute}\\
[4mm]
Third Author\footnote{\href{mailto:third@author }{third@author}}\\
\textit{\small Second Institute}
}
\date{\small Month NN, YYYY}
\begin{document}
%\maketitle
\ReportNumbers{XXX-XXX}

@@

We propose two Higgs doublets model based on the scotogenic model. In this model neutrino masses are radiative and we assume that neutrinos are Dirac fermion. Viable candidates for dark matter are the mediators in the loop. In addition, we propose that the fermionic mediator in the loop be Majorana fermion. This model is restricted by observables of neutrino physics,  lepton flavor violation and cosmological constrain in the number of relativistic degrees of freedom for neutrinos. Here we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$TeV in order to satisfy the conditions of $N_{eff}$..
\end{abstract}

\section{Introduction}
\label{sec:intro}

@@

\section{Neutrinos}
\label{sec:Neutrinos}
%
\begin{figure}
\centering
\includegraphics[scale=0.75]{Figures/Neutrino_Loop.pdf}
\caption{One-loop generation of Dirac neutrino mass}
\label{fig:zee}
\end{figure}
%
 The Dirac neutrino mass matrix in this model is generate to one loop level, which is shown in fig(\ref{fig:zee}). The expression for $\mathcal{M}_{\nu}$ is given by~\cite{Reig:2018mdk}
%
\begin{align}
(\mathcal{M}_{\nu})_{ij} = \frac{\sqrt{2}\mu \upsilon_{2}}{64 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i}^{a} M_{\psi_{a}}y_{j}^{a}}{m_{\chi_{R2}}^{2}-m_{\chi_{R1}}^{2}} \left[ F\left( \frac{m_{\chi_{R2}}^{2}}{M_{\psi_{a}}} \right) - F\left( \frac{m_{\chi_{R1}}^{2}}{M_{\psi_{a}}} \right) \right] + (R \to I)\,,
\end{align}
%
where $F(m_{S_{\beta}}^{2}/M_{\psi}^{2}) = m_{S_{\beta}}^{2}\log(m_{S_{\beta}}^{2}/M_{\psi})/(m_{S_{\beta}}^{2}-M_{\psi})$ is loop function, $M_{\psi_{a}}$ is the fermión mass  and $\chi_{R_(1,2)}$ are the two CP-even mass eigenstate and $\chi_{I_{(1,2)}}$ are two CP-odd mass eigenstate.To obtain neutrino masses it is necessary that $\mu \neq 0$. In addition, To explain the suppression of the mass matrix, it is usually assumed that the mass of the mediator fermions is very large. Another possibility is small values of $\mu$, this suppress the value of the neutrino masses. The structure of the effective neutrino mass matrix is given by the product $(M_{\nu})_{ij} \propto h^{a}_{i} y^{b}_{j}$, which is similar to the structure of the neutrino mass matrix for the tree-level seesaw mechanism for Dirac neutrinos~\cite{Chulia:2016ngi}. If only one fermion $\psi$ is added, we will have two massless neutrinos, which does not agree with the current data obtained from the neutrino experiments~\cite{deSalas:2017kay}. In our case, we will assume the existence of three fermions, generating Dirac scotogenic masses for the two neutrinos ($\nu_{k}$ is massless due to the assignment of charges).

@@

\section{Lepton flavor violation}
\label{sec:LFV}
%
\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/LFV.pdf}
\caption{Feynman diagram for process $l^{-}_{i} \to l^{-}_{j} \gamma$}
\label{fig:LFV}
\end{figure}
%
The new Yukawa interactions in Eq~\eqref{Eq:LagY} in our model introduce processes that violate the leptonic flavor in the charged sector (CLFV). These CLFV processes are induced at one loop level, as shown in the figure~\ref{fig:LFV}. In this case, the $\psi_{a} \widetilde{\eta}^{\dagger} L_{i}$ interaction allows the part of the double scalar $\eta$ ($\eta^{\pm}$) to mediate in the loop.

@@

\section{Cosmological constrain}
\begin{comment}
%
\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/Tdec.pdf}
\includegraphics[scale=0.6]{Figures/Delta_Neff1.pdf}
\caption{One-loop generation of Dirac neutrino mass}
\label{fig:Neff}
\end{figure}
%
\end{comment}

@@

The cross section is given in~\cite{Barger:2003zh}, in the case with heavy mediator $T^{\nu_R}_{dec} \ll M_{Z^{\prime}}$, we can to take the limit when $s \ll M_{Z^{\prime}}$ and neglecting the fermion masse, we have that the cross section is
%
\begin{align*}
    \sigma_{f}(s) \approx N^{C}_{f} \frac{s}{12 \pi} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} Q^{2}_{\nu_R} (Q^{2}_{f_L} + Q^{2}_{f_R})\,,
\end{align*}
%
where $N^{C}_{f}$ is the color multiplicity of the fermion, i.e. $N^{C}_{q(\ell)} = 3(1)$, $Q_{f}$ is the charge of the fermion under the new simmetry, $g^{\prime}$ and $M_{Z^{\prime}}$ are the gauge coupling and mass for the new gauge boson. Solving the integrals with this last cross section we obtain that the interaction rate is given by
%
\begin{align*}
    \Gamma_{\nu_{R}}(T) = \frac{49 \pi^{5} T^{5}}{97200 \zeta(3)} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} \sum_{f} N^{C}_{f} Q^{2}_{f}\,,
\end{align*}
%
%
\begin{figure}
\centering
\includegraphics[scale=0.8]{Figures/DeltaNeff.pdf}
\caption{In the upper panel is the decoupling temperature of the right neutrino $\nu_{R}$ in function of $M_{z^{\prime}}/g^{\prime}$. In the lower panel is the additional contribution to the number of relativistic degrees of freedom ($\Delta N_{eff}$) in function of $M_{z^{\prime}}/g^{\prime}$. The gray shaded region is excluded by the measurements in the Planck CMB~\cite{Aghanim:2018eyx}. The region shaded in violet shows the bound from LEP  LEP~\cite{Alioli:2017nzr}.}
\label{fig:Neff}
\end{figure}
%
where the sum is performed over all SM fermion that are in thermal equilibrium with the plasma at temperature T. To estimate the contribution to relativistic degrees of freedom for neutrinos, it is necessary to calculate the decoupling temperature of the right neutrinos ($T^{\nu_R}_{dec}$). The latter occurs when the interaction rate of neutrinos with the SM drop below the rate of expansion of the universe, i.e.
%
\begin{align*}
\Gamma(T^{\nu_R}_{dec}) = H(T^{\nu_R}_{dec})\,, 
\end{align*}
%
where the Hubble expansion parameter is
%
\begin{align*}
    H(T) = \sqrt{\frac{8 \pi G_{N} \rho(T)}{3}} = \sqrt{\frac{4 \pi^{3} G_{N}}{45} \left( g(T) + \frac{21}{4} \right)} T^{2}\,,
\end{align*}
%
where $21/4$ correspond to the contribution of the right neutrinos to relativistic degrees of freedom. By finding the decoupling temperature of the right neutrinos $T^{\nu_R}_{dec} $ by a root finding method, it is possible to calculate $\Delta N_{eff}$.

@@

\includegraphics[scale=0.9]{Figures/DeltaNeff.pdf}

>>>>

\author{First Author\footnote{\href{mailto:first@author}{first@author}},
Second Author\footnote{\href{mailto:second@author}{second@author}}\\
\textit{\small  First Institute}\\
[4mm]
Third Author\footnote{\href{mailto:third@author }{third@author}}\\
\textit{\small Second Institute}
}
\date{\small Month NN, YYYY}
\begin{document}
\maketitle
\ReportNumbers{XXX-XXX}

@@

We propose a two-Higgs-doublet model (THDM) for one-loop Dirac neutrino masses with Majorana mediators which can be dark matter candidates if they are the lightest states circulating the loop. This model is restricted by  neutrino physics,  lepton flavor violation and cosmological constrains, including  
the effective number light neutrinos $N_{\text{eff}}$ . Here we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60\ \text{TeV}$ in order to satisfy the conditions of $N_{\text{eff}}$..
\end{abstract}

\section{Introduction}
\label{sec:intro}
%Dirac vs Majorana (From previous paper: must be rephrased
The interpretation of neutrino experimental data in terms of neutrino
oscillations is compatible with both Majorana or Dirac neutrino
masses \cite{Tanabashi:2018oca}. The former possibility  has received the most attention but, given the lack of signals in neutrinoless double beta decay experiments
\cite{KamLAND-Zen:2016pfg,Agostini:2018tnm,Aalseth:2017btx,Alduino:2017ehq,Albert:2017owj,Arnold:2016bed}, the latter cannot be dismissed. If neutrinos are Dirac particles, the Standard Model (SM) particle content must be extended with right-handed neutrinos, which can increase the number the effective number light neutrinos, $N_{\text{eff}}$, until 6. To give small masses to at least two Majorana or Dirac neutrinos, as required to explain the neutrino oscillation experiments~\cite{Ahmad:2002jz, Fukuda:1998mi}, the seesaw mechanism with heavy fermions is usually invoked.

and some symmetry must be imposed to prevent their Majorana mass terms.
% Tree-level see-saw with fermionic mediators: Dirac for Dirac, Majorana-Majorana
% One-loop level: Majorana-Majorana, Dirac-Dirac, Majorana-Dirac. Simplest model with Dirac-Majorana still missing
% At one-loop Dark Matter is predicted in model-dependent ways. In this case...

@@

\section{Neutrinos}
\label{sec:Neutrinos}
%
\begin{figure}
\centering
\includegraphics[scale=0.75]{Neutrino_Loop.pdf}
\caption{One-loop generation of Dirac neutrino mass}
\label{fig:zee}
\end{figure}
%
 The Dirac neutrino mass matrix in this model is generate to one loop level, which is shown in fig(\ref{fig:zee}). The expression for $\mathcal{M}_{\nu}$ is given by~\cite{Reig:2018mdk}
%
\begin{align}
(\mathcal{M}_{\nu})_{ij} = \frac{\sqrt{2}\mu \upsilon_{2}}{64 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i}^{a} M_{\psi_{a}}y_{j}^{a}}{m_{\chi_{R2}}^{2}-m_{\chi_{R1}}^{2}} \left[ F\left( \frac{m_{\chi_{R2}}^{2}}{M_{\psi_{a}}} \right) - F\left( \frac{m_{\chi_{R1}}^{2}}{M_{\psi_{a}}} \right) \right] + (R \to I)\,,
\end{align}
%
where $F(m_{S_{\beta}}^{2}/M_{\psi}^{2}) = m_{S_{\beta}}^{2}\log(m_{S_{\beta}}^{2}/M_{\psi})/(m_{S_{\beta}}^{2}-M_{\psi})$ is loop function, $M_{\psi_{a}}$ is the fermión mass  and $\chi_{R_(1,2)}$ are the two CP-even mass eigenstate and $\chi_{I_{(1,2)}}$ are two CP-odd mass eigenstate.To obtain neutrino masses it is necessary that $\mu \neq 0$. In addition, To explain the suppression of the mass matrix, it is usually assumed that the mass of the mediator fermions is very large. Another possibility is small values of $\mu$, this suppress the value of the neutrino masses. The structure of the effective neutrino mass matrix is given by the product $(M_{\nu})_{ij} \propto h^{a}_{i} y^{b}_{j}$, which is similar to the structure of the neutrino mass matrix for the tree-level seesaw mechanism for Dirac neutrinos~\cite{Chulia:2016ngi}. If only one fermion $\psi$ is added, we will have two massless neutrinos, which does not agree with the current data obtained from the neutrino experiments~\cite{deSalas:2017kay}. In our case, we will assume the existence of three fermions, generating Dirac scotogenic masses for the two neutrinos ($\nu_{k}$ is massless due to the assignment of charges).

@@

\section{Lepton flavor violation}
\label{sec:LFV}
%
\begin{figure}
\centering
\includegraphics[scale=0.6]{LFV.pdf}
\caption{Feynman diagram for process $l^{-}_{i} \to l^{-}_{j} \gamma$}
\label{fig:LFV}
\end{figure}
%
The new Yukawa interactions in Eq~\eqref{Eq:LagY} in our model introduce processes that violate the leptonic flavor in the charged sector (CLFV). These CLFV processes are induced at one loop level, as shown in the figure~\ref{fig:LFV}. In this case, the $\psi_{a} \widetilde{\eta}^{\dagger} L_{i}$ interaction allows the part of the double scalar $\eta$ ($\eta^{\pm}$) to mediate in the loop.

@@

\section{Cosmological constrain}
\begin{comment}
%
\begin{figure}
\centering
\includegraphics[scale=0.6]{Tdec.pdf}
\includegraphics[scale=0.6]{Delta_Neff1.pdf}
\caption{One-loop generation of Dirac neutrino mass}
\label{fig:Neff}
\end{figure}
%
\end{comment}

@@

The cross section is given in~\cite{Barger:2003zh}, in the case with heavy mediator $T^{\nu_R}_{dec} \ll M_{Z^{\prime}}$, we can to take the limit when $s \ll M_{Z^{\prime}}$ and neglecting the fermion masse, we have that the cross section is
%
\begin{align*}
    \sigma_{f}(s) \approx N^{C}_{f} \frac{s}{12 \pi} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} Q^{2}_{\nu_R} (Q^{2}_{f_L} + Q^{2}_{f_R})\,,
\end{align*}
%
where $N^{C}_{f}$ is the color multiplicity of the fermion, i.e. $N^{C}_{q(\ell)} = 3(1)$, $Q_{f}$ is the charge of the fermion under the new simmetry, $g^{\prime}$ and $M_{Z^{\prime}}$ are the gauge coupling and mass for the new gauge boson. Solving the integrals with this last cross section we obtain that the interaction rate is given by
%
\begin{align*}
    \Gamma_{\nu_{R}}(T) = \frac{49 \pi^{5} T^{5}}{97200 \zeta(3)} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} \sum_{f} N^{C}_{f} Q^{2}_{f}\,,
\end{align*}
%
%
\begin{figure}
\centering
\includegraphics[scale=0.8]{DeltaNeff.pdf}
\caption{In the upper panel is the decoupling temperature of the right neutrino $\nu_{R}$ in function of $M_{z^{\prime}}/g^{\prime}$. In the lower panel is the additional contribution to the number of relativistic degrees of freedom ($\Delta N_{eff}$) in function of $M_{z^{\prime}}/g^{\prime}$. The gray shaded region is excluded by the measurements in the Planck CMB~\cite{Aghanim:2018eyx}. The region shaded in violet shows the bound from LEP  LEP~\cite{Alioli:2017nzr}.}
\label{fig:Neff}
\end{figure}
%
where the sum is performed over all SM fermion that are in thermal equilibrium with the plasma at temperature T. To estimate the contribution to relativistic degrees of freedom for neutrinos, it is necessary to calculate the decoupling temperature of the right neutrinos ($T^{\nu_R}_{dec}$). The latter occurs when the interaction rate of neutrinos with the SM drop below the rate of expansion of the universe, i.e.
%
\begin{align*}
\Gamma(T^{\nu_R}_{dec}) = H(T^{\nu_R}_{dec})\,, 
\end{align*}
%
where the Hubble expansion parameter is
%
\begin{align*}
    H(T) = \sqrt{\frac{8 \pi G_{N} \rho(T)}{3}} = \sqrt{\frac{4 \pi^{3} G_{N}}{45} \left( g(T) + \frac{21}{4} \right)} T^{2}\,,
\end{align*}
%
where $21/4$ correspond to the contribution of the right neutrinos to relativistic degrees of freedom. By finding the decoupling temperature of the right neutrinos $T^{\nu_R}_{dec} $ by a root finding method, it is possible to calculate $\Delta N_{eff}$.

@@

\includegraphics[scale=0.9]{DeltaNeff.pdf}
